Ceph Parallel File System Evaluation Report

### 2013-11-06 background.tex
fixing based on various review comments

\section{Introduction}

Oak Ridge Leadership Computing Facility (OLCF)\footnote{This research was
supported by, and used the resources of, the Oak Ridge Leadership Computing
Facility, located in the National Center for Computational Sciences at ORNL,
which is managed by UT Battelle, LLC for the U.S. DOE (under the contract No.
DE-AC05-00OR22725).} at Oak Ridge National Laboratory (ORNL) has a long history
of deploying and running very-large-scale high-performance computing (HPC)
systems. 
%The facility hosted
%the Jaguar supercomputer up until recently, which was upgraded to the Titan
%supercomputer. 
In order to satisfy the I/O demand of such supercomputers, OLCF
also hosts large-scale file and storage systems. Lustre has been OLCF's choice
as the distributed parallel file system.  
%The latest such
%large-scale file systems is Spider II\cite{spider2}.  Spider II, deployed in
%2013, is designed to operate at over 1 TB/s peak aggregate I/O throughput and
%has a 40 PB of raw disk capacity. As the scratch 
%file system for Titan, a leadership computing platform,
%Spider II emphasizes \textit{capability} over \textit{capacity}. 
However, we
recognize that there are a wide variety of scientific data and emerging
workloads with different performance and data access requirements (e.g., RESTful
interface, S3-like API, cloud solution integration) which might not be
efficiently serviced by Lustre. OLCF is constantly evaluating new and emerging
file and storage system technologies.

This paper presents our file and block I/O performance and scalability
evaluation of Ceph for scientific high-performance computing (HPC)
environments. Through systematic experiments and tuning efforts, we are able
to observe Ceph performing close to 80\% of raw hardware bandwidth at object
level and close to 70\% of at file system level.

\section{Background}

@@

Data objects are distributed across storage daemons (ceph-osd) using
CRUSH\cite{Weil:2006:Crush}, a deterministic hashing function that allows
administrators to define flexible placement policies over a hierarchical
cluster structure (e.g., disks, hosts, racks, rows, datacenters).  The
location of objects can be calculated based on the object identifier and
cluster layout (similar to consistent hashing~\cite{karger1997consistent}),
thus there is no need for a metadata index or server for the RADOS object store.
%Further, because CRUSH provides an authoritative view of data placement,
%storage daemons can coordinate directly to handle data replications, recovery,
%or object migration in the face of failure or cluster topology changes.  
A small cluster of monitors (ceph-mon daemons) use Paxos to provide consensus on
the current cluster layout, but do not need to explicitly coordinate migration
or recovery activities.

@@

While we are interested in Ceph for its ability to support
alternative workloads that are not easily accomplished with Lustre, in this
study we are investigating the use Ceph for future
large-scale scientific HPC storage deployments. This paper presents our
experience, results, and observations in measuring the scalability and
performance of Ceph for capability workloads.  Additionally, Ceph is under
rapid development, and in  between releases, we often
experienced different stability and performance outcomes.  
%We will try to make
%clear in the writing when such changes occurred.
%As interesting and feature-rich as Ceph may be,  scalability and performance
%are our top priorities due to the unique requirements our environment.  As part
%of this study, we set up a dedicated testbed within OLCF to  evaluate Ceph.
%Our goal was to investigate the feasibility of using the Ceph for future
%large-scale scientific HPC storage deployments. This paper presents our
%experience, results, and observations.  While evaluating our results, please
%keep in mind that Ceph is still a relatively \textit{young} parallel file
%system and its code base is changing rapidly. In between releases, we often
%experienced different stability and performance outcomes.  We will try to make
%clear in the writing when such changes occurred.

>>>>

\section{Background}
\label{sec:background}

@@

Data objects are distributed across Object Storage Devices (OSD), which refers
to either physical or logical storage unit, using CRUSH\cite{Weil:2006:Crush},
a deterministic hashing function that allows administrators to define flexible
placement policies over a hierarchical cluster structure (e.g., disks, hosts,
racks, rows, datacenters).  The location of objects can be calculated based on
the object identifier and cluster layout (similar to consistent
hashing~\cite{karger1997consistent}), thus there is no need for a metadata
index or server for the RADOS object store.
%Further, because CRUSH provides an authoritative view of data placement,
%storage daemons can coordinate directly to handle data replications,
%recovery, or object migration in the face of failure or cluster topology
%changes.  
A small cluster of monitors (ceph-mon daemons) use Paxos to provide consensus
on the current cluster layout, but do not need to explicitly coordinate
migration or recovery activities.

@@

While we are interested in Ceph for its ability to support alternative
workloads that are not easily accomplished with Lustre, in this study we are
investigating the use Ceph for future large-scale scientific HPC storage
deployments. This paper presents our experience, results, and observations in
measuring the scalability and performance of Ceph.

%Additionally, Ceph is under
%rapid development, and in between releases, we often
%experienced different stability and performance outcomes.  
%We will try to make
%clear in the writing when such changes occurred.
%As interesting and feature-rich as Ceph may be,  scalability and performance
%are our top priorities due to the unique requirements our environment.  As part
%of this study, we set up a dedicated testbed within OLCF to  evaluate Ceph.
%Our goal was to investigate the feasibility of using the Ceph for future
%large-scale scientific HPC storage deployments. This paper presents our
%experience, results, and observations.  While evaluating our results, please
%keep in mind that Ceph is still a relatively \textit{young} parallel file
%system and its code base is changing rapidly. In between releases, we often
%experienced different stability and performance outcomes.  We will try to make
%clear in the writing when such changes occurred.

### 2013-11-06 ceph-tuning.tex
fixing based on various review comments

\section{Further Optimization and Improvements}
\label{sec:ceph-tuning}

@@

\begin{figure}[h]
\centering
\includegraphics[width=3.5in]{parametric}
\caption{Evaluating parameter impact through sweeping test}
\label{fig:parametric}
\end{figure}

After the initial test results, we tried various combinations of tweaks
including changing the number of filestore op threads, putting all of the
journals on the same disks as the data, doubling the OSD count, and upgrading
Ceph to a development version which reduces the seek overhead caused by
\texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are now
included as of the Ceph Cuttlefish release, v0.61).  The two biggest
improvements resulted from disabling CRC32c checksums and increasing the OSD
count on the server.  With these changes, we are seeing better results.

We swept over Ceph configuration parameters to examine how different tuning
options affect performance on the DDN platform. The result of this parameter
probing is illustrated in Figure~\ref{fig:parametric}. Please refer to
Appendix E of \cite{ceph:techreport} for explanations of these probed
parameters.

As a result of this testing, we improved performance slightly by
increasing the size of various Ceph buffers and queues, enabling AIO journals,
and increasing the number of OSD op threads.

@@

\begin{figure}[htb]
\centering
%\includegraphics[width=3.5in]{ior-client-no-crc32}
\includegraphics[width=3.5in]{ior_no_crc}
\caption{IOR test with disabling client-side CRC32}
\label{fig:ior-no-client-crc32}
\end{figure}

@@

Additionally, we increased the size of the CephFS kernel client's read-ahead
chance.  
%IOR results reflecting the read-ahead cache size change are presented
%in Figure~\ref{fig:ior-kernel-39}.

>>>>

\section{Further Optimization \\and Improvements}
\label{sec:ceph-tuning}

@@

\begin{figure}[h]
\centering
\includegraphics[width=3.5in]{para2}
%\includegraphics[width=3.5in]{parametric}
\caption{Evaluating parameter impact through sweeping test}
\label{fig:parametric}
\end{figure}

After the initial test results, we tried various combinations of tweaks
including: changing the number of filestore op threads, putting all of the
journals on the same disks as the data, doubling the OSD count, and upgrading
Ceph to a development version which reduces the seek overhead caused by
\texttt{pginfo} and \texttt{pglog} updates on XFS (these enhancements are now
included as of the Ceph Cuttlefish release, v0.61).

%The two biggest
%improvements resulted from disabling CRC32c checksums and increasing the OSD
%count on the server.  With these changes, we are seeing better results.

We swept over Ceph configuration parameters to examine how different tuning
options affect performance on the DDN platform. The result of this parameter
probing is illustrated in Figure~\ref{fig:parametric}. Please refer to
Appendix E of \cite{ceph:techreport} for explanations of these probed
parameters. In this figure, the default is where we started with. Reads
benefit from increasing the \verb!osd_op_threads! (4 and 8), with 7.3\% and
9\% improvement respectively. For writes, the substantial boost comes with
\verb!journal_aio! true and \verb!big_bytes!, with 11.5\% and 16.3\%
improvement respectively. Other probed parameters (not shown on this figure)
doesn't bear tangible impacts.

%As a result of this testing, we improved performance slightly by
%increasing the size of various Ceph buffers and queues, enabling AIO journals,
%and increasing the number of OSD op threads.

@@

\begin{figure}[htb]
\centering
%\includegraphics[width=3.5in]{ior-client-no-crc32}
%\includegraphics[width=3.5in]{ior_no_crc}
\includegraphics[width=3.5in]{crc32}
\caption{Impact of Disabling CRC32}
\label{fig:ior-no-client-crc32}
\end{figure}

@@

Additionally, we increased the size of the CephFS kernel client's read-ahead
cache.  
%IOR results reflecting the read-ahead cache size change are presented in
%Figure~\ref{fig:ior-kernel-39}.
